\documentclass[preprint]{sigplanconf}

\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage[scaled=0.80]{beramono}
\usepackage{amsmath}
\usepackage{stmaryrd}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{listings}
\usepackage{url}
\usepackage{mathtools}
\usepackage{mathpartir}
\usepackage{booktabs}
\usepackage[small,compact]{titlesec}

\addtolength{\floatsep}{-1.2mm}
\addtolength{\textfloatsep}{-1.2mm}
\addtolength{\dbltextfloatsep}{-1.2mm}

%\newcommand{\code}[1]{{\scriptsize {\tt #1}}}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\judge}{\vdash}
\newcommand{\Implies}{\Rightarrow}
\newcommand{\Section}{\S}

% Comment out lineno for final draft.
\usepackage{lineno}
%\linenumbers

% JavaScript language definition.
\lstdefinelanguage{JavaScript}
{morekeywords={var,let,function,new,if,else,switch,while,catch,try,finally,throw,true,false,eval,with,undefined,case,default,do,break,for,in,continue,return},
  keywordstyle=\ttfamily\bfseries,
  sensitive=false,
  comment=[l]{//},
  morestring=[b]",
  morestring=[b]',
  mathescape=true,
  numbers=left,
  numberstyle=\small}
\lstset{captionpos=t,xleftmargin=5pt,columns=flexible,basicstyle=\ttfamily,showstringspaces=false,escapechar=\#,language=JavaScript}

\title{Fast and Precise Hybrid Type Inference for JavaScript}
% Author info left blank for double blind submission.
\authorinfo{}{}{}

\begin{document}

\maketitle

\begin{abstract}
JavaScript performance is often bound by its dynamically typed
nature. Compilers do not have access to static type information, making
generation of efficient, type-specialized machine code difficult.
We seek to solve this problem
by inferring types. In this paper we present a hybrid type inference algorithm for
JavaScript based on points-to analysis. Our algorithm is \emph{fast}, in that
it pays for itself in the optimizations it enables.  Our algorithm is also
\emph{precise}, generating information that closely reflects the program's
actual behavior even when analyzing polymorphic code,
by augmenting static analysis with run-time type barriers.

We showcase an implementation for Mozilla Firefox's JavaScript engine,
demonstrating both performance gains and viability.
Through integration with the just-in-time (JIT) compiler in Firefox, we have improved
performance on major benchmarks and JavaScript-heavy websites by up to 50\%.
Inference-enabled compilation is scheduled to become the default compilation mode in Firefox 9.
\end{abstract}

\input{example.tex}
\input{analysis.tex}
\input{implementation.tex}
\input{evaluation.tex}
\input{related-work.tex}

\section{Conclusion and Future Work}
\label{sec:conclusion}

We have described a hybrid type inference algorithm that is both fast and
precise using constraint-based static analysis and runtime checks. Our
production-quality implementation integrated with the JavaScript JIT compiler
inside Firefox has demonstrated the analysis to be both effective and
viable. We have presented compelling empirical results: the analysis
enables generation of much faster code, and infers precise information on
both benchmarks and real websites.

We hope to look more closely at type barriers in the future with the aim to
reduce their frequency without degrading precision. We also hope to
look at capturing more formally the hybrid nature of our algorithm.
\\
\\
{\noindent
\textbf{Acknowledgements.}
We thank the Mozilla JavaScript team, Todd Millstein, Jens Palsberg, Sam
Tobin-Hochstadt, and Alex Aiken for draft reading and helpful discussion.

\bibliographystyle{abbrvnat}
\bibliography{citations}{}

\end{document}
