\appendix

\section{Methodology}
\label{app:methodology}

Data in \Section\ref{sec:websites} was collected manually using a modified
version of Firefox which had instrumentation to track several metrics. We
restart the browser after collecting numbers for each website. The browser is
always started with the \code{-private} flag, which generates a new
profile. Each website is profiled two times.

The procedures used with each website, game, or demo are detailed below. In
general, demos and animations are played through in their entirety with no
user interaction, and we used interactive websites in---what we hope to
be---an average manner.

\subsection{Websites}

\begin{description}
\item[gmail] (\url{http://mail.google.com})

\item[googlemaps] (\url{http://maps.google.com})

\item[facebook] (\url{http://www.facebook.com})

  For Facebook, we registered a test user for the purpose of profiling who has
  one of the authors on its friends list.
  \begin{enumerate}
  \item Sign in with the test user.
  \item Search for ``John''; wait until ``John Coyle'' shows up, press enter.
  \item Search for ``John'' again, but click on the magnifying glass to get a list.
  \item Click on See More Results.
  \item Click on the Facebook logo.
  \item Search for Mozilla Firefox and go to the page.
  \item Click on Photos.
  \item Click on Wall Photos.
  \item Click on the first picture.
  \item Click on the right arrow 5 times.
  \item Click on each of the 3 dimmed out icons next to the Facebook logo.
  \item Click on back twice from Wall Photos to get back to the Firefox page.
  \item Click on Like, then cancel the Security Check.
  \end{enumerate}
\item[flickr] (\url{http://www.flickr.com})

  \begin{enumerate}
  \item Click on Explore
  \item Choose October 2011.
  \item Click on the 3rd, choose the first picture.
  \item Press L to enter Lightbox.
  \item Click on Older arrow 15 times.
  \item Click View All Sizes.
  \item Search for Firefox.
  \end{enumerate}
\item[grooveshark] (\url{http://www.grooveshark.com})

  \begin{enumerate}
  \item Search for ``Kavinsky''.
  \item Play ``Kavinsky - Nightcall'' for 15 seconds.
  \item Pause.
  \item Click on Popular.
  \item Click on Classical.
  \item Click on Start Radio.
  \item Play for 1.5 minutes.
  \item Pause.
  \item Search for ``No Children''.
  \item Queue Mountain Goats - No Children and play for 1 minute.
  \end{enumerate}
\item[meebo] (\url{http://www.meebo.com})

  Meebo is an instant messenger client in the browser. For the purpose of
  profiling one of the authors signed in using his personal AIM account and
  sent messages to himself on the client.
  \begin{enumerate}
  \item Click on the AIM logo.
  \item Sign in with personal AIM account.
  \item Send messages of random lengths to self for 2 minutes.
  \item Drag the message window to the four corners of the browser window, clockwise.
  \end{enumerate}
\item[reddit] (\url{http://reddit.com})

  \begin{enumerate}
  \item Click on Pics.
  \item Click on Funny.
  \item Click on Politics.
  \item Click on Gaming.
  \item In Gaming, click on the New tab.
  \item Click on the Controversial tab.
  \item Click on the Top tab.
  \item Click on the Saved tab.
  \item Click on Pics.
  \item Click on comments of first link.
  \item Change sorted by to Hot.
  \end{enumerate}
\item[youtube] (\url{http://www.youtube.com})

  \begin{enumerate}
  \item Scroll to bottom and click on Try something new!
  \item Try out HTML5 Video, click Join.
  \item Search for ``Rowlf the Dog''.
  \item Scroll down to ``Cottleston Pie''.
  \item Play the video in its entirety.
  \item Click Next on the Next link underneath the comments.
  \end{enumerate}
\item[280slides] (\url{http://208slides.com})

  \begin{enumerate}
  \item Click on Try for Free.
  \item Click on Take a Tour.
  \item Click through each page.
  \item Go back to slide 1, click on Present.
  \item Right arrow through end of show, click to exit.
  \item Change Theme to Black.
  \item While still on slide 1, click on Shapes.
  \item Double click on Square, Circle, Triangle, in that order.
  \item Exit Media Browser.
  \item Go to slide 2, change ``Getting Started'' to ``Test''.
  \item Click on New Slide 2 times, then delete both.
  \end{enumerate}
\end{description}

\subsection{Games and Demos}
\begin{description}
\item[angrybirds] (\url{http://chrome.angrybirds.com})

  Play game for 5-6 levels.
\item[bullet] (\url{http://www.syntensity.com/static/bullet.html})

  Watch cubes fall 5 times.
\item[lights] (\url{http://lights.elliegoulding.com})

  Play in entirety.
\item[FOTN]
\item[monalisa]
\item[ztype] (\url{http://www.phoboslab.org/ztype})

  \begin{enumerate}
  \item Play Expert mode for 5 waves.
  \item Type nothing on wave 6 and die.
  \end{enumerate}
\end{description}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "main"
%%% End: 